```{r}
options(tidyverse.quiet = TRUE)
library(tidyverse)
library(VIM) #visualizing missingness
library(mice)
install.packages("skimr")
library(skimr) #alternative way to view dataset summaries
```

Read in dataset   
```{r}
grades = read_csv("class-grades.csv")
```

```{r}
str(grades)
summary(grades)
skim(grades)
```
## Question 1: For which variables is there missing data?
## Tutorial, Midterm, TakeHome, Final

# Looking at missingness by variable and combinations of missingness using "aggr" from VIM package.  
```{r}
vim_plot = aggr(grades, numbers = TRUE, prop = c(TRUE, FALSE),cex.axis= 1)
#the cex.axis reduces size of text on x-axis so labels fit better
```
## Question 2: Use the VIM package to visualize missingness. Are there any students that are missing multiple pieces of data?
## Yes?

# Row-wise deletion of any row with at least one NA:
```{r}
grades_rowdel = grades %>% drop_na() 
#alternatively can specify which variable(s) on which to do the drop_na
#drop_na(Age)
skim(grades_rowdel)
```
## Question 3: Use row-wise deletion of missing values to create a new data frame. How many rows remain in this data frame?
## 89 Rows Remain

Column-wise deletion of the "Age" variable (creating a new data frame with this variable removed).  
```{r}
grades_coldel = grades %>% select(-) 
vim_plot = aggr(grades_coldel, numbers = TRUE, prop = c(TRUE, FALSE),cex.axis=1)
skim(grades_coldel)
```
## Question 4: Use column-wise deletion of missing values to create a new data frame (from the original data frame not from the data frame created in Task 3). How many columns remain in this data frame?
## 2

## Question 5: Which approach (Task 3 or Task 4) seems preferable for this dataset? Briefly discuss your answer.
## Task 3, using Task 4 or "Column wise would remove entire columns or categories from the dataset. I would rather lose rows of data to have a more complete view of the remaining data.

Imputation. Let's use the "mice" package to do imputation.  
```{r}
set.seed(123) #sets seed for random number generator
imp_grades = mice(grades, m=5, method='pmm', printFlag=FALSE)
#m is the number of imputations, 5 is a reasonable value as a default
#pmm is "predictive mean matching" = imputation method for numeric data
#printFlag reduces amount of output
summary(imp_grades)
```

```{r}
densityplot(imp_grades, ~Final) #red imputed, blue original
```
Merge the imputed values into our titanic data frame  
```{r}
grades_complete = complete(imp_grades) 
summary(grades_complete)
```

## Question 6: Use the “mice” package to impute the missing data in this dataset. Set “m = 5” and “method =”pmm"" in the imputation. You MUST use a random number seed of 123 for this imputation. What is the mean value for the “Final” variable after imputation?
## The mean value for the “Final” variable after imputation is 68.33



