
```{r}
library(tidyverse) #tidyverse set of packages and functions
library(tidymodels)
library(glmnet) #for Lasso, ridge, and elastic net models 
library(GGally) #create ggcorr and ggpairs plots
library(ggcorrplot) #create an alternative to ggcorr plots
library(MASS) #access to forward and backward selection algorithms
library(lubridate)
library(lmtest) #for the dw test
library(splines) #for nonlinear fitting
library(car) #for calculating the variance inflation factor
```

```{r}
bike = read_csv("bike_cleaned.csv")
summary(bike)
```

```{r mdy mutate}
bike = bike %>% mutate(dteday = mdy(dteday))
#Note that mdy is a lubridate package function
#You can read more about lubridate here: https://lubridate.tidyverse.org/
```

```{r variable to factor}
bike = bike %>% mutate_if(is.character, as_factor)
```

```{r hr to factor}
bike = bike %>% mutate(hr = as_factor(hr))
```

```{r}
ggcorr(bike, label = "TRUE", label_round = 2) 
```
# Which is best correlated with Count? D. Temp

```{r hr/count}
ggplot(bike,aes(x=hr,y=count)) + geom_boxplot() + geom_jitter(alpha = 0.15) + theme_bw()
```

```{r}
ggplot(bike,aes(x=season,y=count)) + geom_boxplot() + geom_jitter(alpha = 0.15) + theme_bw()
```
# Summer appears to have the highest count of rides

```{r}
bike_recipe = recipe(count ~ hr,bike)

lm_model = #give the model type a name 
  linear_reg() %>% #specify that we are doing linear regression
  set_engine("lm") #specify the specify type of linear tool we want to use 

lm_wflow = 
  workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(bike_recipe)

lm_fit = fit(lm_wflow, bike)
```

```{r}
summary(lm_fit$fit$fit$fit)
```
# 23 dummy variables are used to represent hr in the model
# hr1 is the base level?
# hr17 has the highest number of rides

```{r}
ggplot(bike, aes(x=temp, y=count)) + geom_point() + geom_smooth(method = lm, se = FALSE) + theme_bw()
```
# A. As “temp” increases, “count” appears to generally increase.

```{r hr/temp to predict count}
bike_recipe = recipe(count ~ hr + temp, bike)

lm_model = #give the model type a name 
  linear_reg() %>% #specify that we are doing linear regression
  set_engine("lm") #specify the specify type of linear tool we want to use 

lm_wflow = 
  workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(bike_recipe)

lm_fit2 = fit(lm_wflow, bike)
```

```{r}
summary(lm_fit2$fit$fit$fit)
```
# What is the value of the slope coefficient for “hr23” in this model (to three decimal places)? 31.748
# Adjusted R-Squared = 0.5886

```{r}
bike_recipe = recipe(count ~ temp + atemp, bike)

lm_model = #give the model type a name 
  linear_reg() %>% #specify that we are doing linear regression
  set_engine("lm") #specify the specify type of linear tool we want to use 

lm_wflow = 
  workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(bike_recipe)

lm_fit3 = fit(lm_wflow, bike)
```

```{r}
summary(lm_fit3$fit$fit$fit)
```
# Adjusted R-Squared = 0.1638
# A. Temp only
# C. Multicollinearity

```{r}
allmod = lm(count ~ season + mnth + hr + holiday + weekday + workingday + weathersit + temp + atemp + hum + windspeed, bike) #use the ~. to include all predictors rather than typing them all in
summary(allmod)
```
# Which two variables combine to make “workingday”?  B.weekday and holiday

```{r}
#backward
backmod = stepAIC(allmod, direction = "backward", trace = TRUE) #trace = TRUE shows how the model is built (which variables are removed)
summary(backmod)
```
# The backward stepwise method removes only one variable. Which variable is removed? B. workingday










