---
title: "Simple Linear Regression and Correlation"
author: "Matthew Overcash"
date: "`r Sys.Date()`"
output: html_document
---
# Module 2 - Assignment 1
## Overcash, Matthew
### Simple Linear Regression and Correlation

```{r Libraries}
library(tidyverse)
library(tidymodels)
library(GGally)
library(lmtest)
library(datasets)
```

```{r air}
air <- data.frame(airquality)

```

```{r Questions}
print(nrow(air))
print(ncol(air))
str(air) #all variables numeric
summary(air) #no missingness
```

```{r remove missing data}
air2 = air %>% drop_na()
str(air2) #all variables numeric
summary(air2) #no missingness
```

```{r Questions Continued}
print(nrow(air2))
print(ncol(air2))
```

```{r}
ggpairs(air2)
```
## Temp is most strongly correlated
## Day is least strongly correlated
## As Temp Increases, Ozone Increases

```{r Linear Regression}
airrecipe = recipe(Ozone ~ Temp, air2)

lm_model = linear_reg() %>% set_engine("lm")

lm_workflow = workflow() %>% add_model(lm_model) %>% add_recipe(airrecipe)
```

```{r}
lm_fit = fit(lm_workflow,air2)
```

```{r}
summary(lm_fit$fit$fit$fit)
```
## 2.4391 is the slope. Look at the Estimate for Temp
## 0.488 is the R-squared value
## The "Temp" variables is significant to the model

```{r}
confint(lm_fit$fit$fit$fit)
```
## True, A 95% confidence interval for the slope coefficient does not contain zero.

```{r}
Temp_Prediction = data.frame(Temp = c(80))
predict(lm_fit, new_data = Temp_Prediction)
```
## Predicted Ozone is 47.50

```{r}
dwtest(lm_fit$fit$fit$fit)
```
## True. There is no evidence of non-independent (autocorrelated) residuals.

