Libraries  
```{r}
library(tidyverse)
library(tidymodels)
library(lubridate)
```

Read-in dataset  
```{r}
bike = read_csv("bike_cleaned.csv")
```

```{r mdy mutate}
bike = bike %>% mutate(dteday = mdy(dteday))
#Note that mdy is a lubridate package function
#You can read more about lubridate here: https://lubridate.tidyverse.org/
```

```{r variable to factor}
bike = bike %>% mutate_if(is.character, as_factor)
```

```{r hr to factor}
bike = bike %>% mutate(hr = as_factor(hr))
```

Split the data (training and testing). 70% of the data to training. Stratified the random split by the response variable "count". 
```{r}
set.seed(1234)
bike_split = initial_split(bike, prop = 0.70, strata = count)
train = training(bike_split)
test = testing(bike_split)
```

```{r}
folds = vfold_cv(train, v = 10)
```

```{r Rows in Training Set}
print(nrow(train))
```
## Question 1: How many rows of data are in the training set?
## 12,163


## Question 2: Stratifying the split by the “count” variable serves what purpose?
## B. Stratifying by “count” ensures that “count” is similarly represented in both the training and testing sets

Linear Regression Model  
```{r}
training_recipe = recipe(count ~ season + mnth + hr + holiday + weekday + temp + weathersit, train)

lm_model = #give the model type a name 
  linear_reg() %>% #specify that we are doing linear regression
  set_engine("lm") #specify the specify type of linear tool we want to use 

lm_wflow = 
  workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(training_recipe)

lm_fit = fit(lm_wflow, train)
```

```{r}
summary(lm_fit$fit$fit$fit)
```
## Question 3: What is the adjusted R-squared value (to four digits) of the resulting model?
## 0.6209

## Question 4:Select the statements below that are likely true about the distribution of predictions?
## C. Some predictions for the number of rides in an hour are negative

See the results on the training set  
```{r}
lm_fit %>% predict(train) %>% bind_cols(train) %>% metrics(truth = count, estimate = .pred)
```

See the results on the test set  
```{r}
lm_fit %>% predict(test) %>% bind_cols(test) %>% metrics(truth = count, estimate = .pred)
```

## Question 5: What is the R-squared value (to four decimal places) of your model on the testing set?
## R-Squared = 0.632  Adjusted R-Squared = 0.6287


